Analysis for Biracial Grade Retention Project

### 2022-09-02 analysis/analysis.Rmd
Save the tbl_resources object

tbl_resources %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Resource differences by race. Shading indicates biracial group.",
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race","mean family income","% own home",
                  "% mother, BA degree","% father, BA degree",
                  "% foreign-born","% either parent foreign-born",
                  "% speak English well", "% Both parents speak english well",
                  "% held back, counterfactual")) %>%
  kable_paper() %>%
  row_spec(index_biracial, background = "#D3D3D3")
```

>>>>

tbl_resources %>%
  mutate_if(is.numeric, format, big.mark=",") %>%
  kbl(caption="Resource differences by race. Shading indicates biracial group.",
      align = c("l",rep("r", ncol(tbl_summary)-1)),
      col.names=c("race","mean family income","% own home",
                  "% mother, BA degree","% father, BA degree",
                  "% foreign-born","% either parent foreign-born",
                  "% speak English well", "% Both parents speak english well",
                  "% held back, counterfactual")) %>%
  kable_paper() %>%
  row_spec(index_biracial, background = "#D3D3D3")

save(tbl_resources, file=here("analysis","output","tbl_resources.RData"))
```
